---
title: "Pluck Tables from KTEA-3"
params:
  patient: Biggie
  test:
    label: "Test"
    value: ktea3
    input: select
    multiple: no
    choices:
      - ktea3
      - ktea3_form_a
      - ktea3_form_b
  test_name:
    label: "Test Name"
    value: "KTEA-3"
    input: select
    multiple: no
    choices:
      - "KTEA-3"
  file:
    label: "No file selected"
    value: file
    input: file
  pages: [12, 13]
  table1:
    label: "Table 1: Core Composite Score Summary"
    value: ""
    input: select
    multiple: yes
    choices:
      ACADEMIC SKILLS:
      - Math Concepts & Applications
      - Letter & Word Recognition
      - Written Expression
      - Math Computation
      - Spelling
      - Reading Comprehension
      READING:
      - Reading Composite
      - Letter & Word Recognition
      - Reading Comprehension
      MATH:
      - Math Composite
      - Math Concepts & Applications
      - Math Computation
      WRITING:
      - Written Language Composite
      - Written Expression
      - Spelling
  table2:
    label: "Table 2: Supplemental Composite Score Summary"
    value: ""
    input: select
    multiple: yes
    choices:
      Sound-Symbol Composite: #todo
      - Basic Reading
      - Pseudoword Decoding
      - Phonemic Proficiency
      - Word Reading
      DECODING:
      - Decoding
      - Pseudoword Decoding2
      - Word Reading2
      READING FLUENCY:
      - Reading Fluency
      - Oral Reading Fluency
      - Orthographic Fluency
      - Decoding Fluency
      PHONOLOGICAL PROCESSING:
      - Phonological Processing
      - Pseudoword Decoding3
      - Phonemic Proficiency2
      ORTHOGRAPHIC PROCESSING:
      - Orthographic Processing
      - Orthographic Fluency2
      - Spelling
      DYSLEXIA INDEX:
      - Dyslexia Index
      - Word Reading3
      - Pseudoword Decoding4
      - Orthographic Fluency3
      OTHER:
      - Orthographic Processing Extended
      - Orthographic Choice
      - Math Fluency
      - Math Fluency-Addition
      - Math Fluency-Subtraction
      - Math Fluency-Multiplication
      - Oral Language
      - Listening Comprehension
      - Oral Expression
  colnames:
    label: "Column Names"
    value: [scale, raw_score, score, ci_95, percentile, category, age_equiv, grade_equiv, gsv]
    input: select
    multiple: yes
    choices:
      - scale
      - raw_score
      - score
      - ci_95
      - percentile
      - category
      - age_equiv
      - grade_equiv
      - gsv
  keep:
    label: "Variables to Keep"
    value: [scale, raw_score, score, percentile, ci_95]
    input: select
    multiple: yes
    choices:
      - scale
      - raw_score
      - score
      - percentile
      - ci_95
---

# KTEA-3

## Load libraries

```{r setup, include=FALSE}
Sys.setenv(JAVA_HOME = "/Library/Java/JavaVirtualMachines/graalvm-community-openjdk-22.0.1+8.1/Contents/Home")
options(java.parameters = "-Xmx16000m")
library(knitr)
library(xfun)
knitr::opts_chunk$set(
  root.dir = normalizePath("./"),
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  error = TRUE
)
library(DT)
library(fs)
library(glue)
library(hablar)
library(here)
library(magrittr)
library(miniUI)
library(pdftools)
library(rJava)
library(shiny)
library(tabulapdf)
library(tibble)
library(tidyverse)
library(bwu)
```

## Test

```{r test}
test <- "ktea3"
test_name <- "KTEA-3"
```

## Patient initials

```{r patient}
patient <- "Biggie"
```

## Pages

```{r pages}
pages <- c(12,13) # move these to yaml
```

## Load text/csv file and save as file.path

```{r file}
input_file_path <- file.choose()
saveRDS(input_file_path, "ktea3.rds")
# input_file_path <- file.path(params$file)
```

## UseThis - updated July 2024

```{r}
# This works well so far
ktea3 <- tabulapdf::extract_tables(
  file = input_file_path,
  pages = pages,
  output = "matrix",
  guess = TRUE
)
table1 <- data.table::as.data.table(ktea3[[1]])
table2 <- data.table::as.data.table(ktea3[[2]])
```

# Tidy Tables

## Column names

```{r}
colnames <- c(
  "scale",
  "raw_score",
  "sum_subtest",
  "score",
  "ci_95",
  "percentile",
  "category",
  "age_equiv",
  "gsv"
) # todo: move this to yaml
```

## Convert to tibble and format

```{r}
library(tibble)
table1 <- as.tibble(table1)
table1 <- table1 |> slice(-1,-2)
table1[1, 1] <- c("Academic Skills Battery (ASB) Composite")
colnames(table1) <- colnames

table1$raw_score <- as.numeric(table1$raw_score, na.rm = TRUE)
table1$sum_subtest <- as.numeric(table1$sum_subtest, na.rm = TRUE)
table1$score <- as.numeric(table1$score, na.rm = TRUE)
table1$percentile <- as.numeric(table1$percentile, na.rm = TRUE)
table1$gsv <- as.numeric(table1$gsv, na.rm = TRUE)
```

```{r}
table2 <- as.tibble(table2)
table2 <- table2 |> slice(-1,-2)
colnames(table2) <- colnames

table2$raw_score <- as.numeric(table2$raw_score, na.rm = TRUE)
table2$sum_subtest <- as.numeric(table2$sum_subtest, na.rm = TRUE)
table2$score <- as.numeric(table2$score, na.rm = TRUE)
table2$percentile <- as.numeric(table2$percentile, na.rm = TRUE)
table2$gsv <- as.numeric(table2$gsv, na.rm = TRUE)
```

## Select variables to keep

```{r}
keep <- c("scale", "raw_score", "score", "ci_95", "percentile", "age_equiv")
table1 <- table1 |> dplyr::select(all_of(keep))
table2 <- table2 |> dplyr::select(all_of(keep))
```

# Mutate

## Make columns

```{r mutate1}
table1 <- bwu::gpluck_make_columns(
  table1,
  range = "",
  test = "ktea3",
  test_name = "KTEA-3",
  domain = "Academic Skills",
  subdomain = "",
  narrow = "",
  pass = "",
  verbal = "Verbal",
  timed = "Untimed",
  test_type = "npsych_test",
  score_type = "standard_score",
  description = "",
  result = ""
)
```

```{r}
table2 <- bwu::gpluck_make_columns(
  table2,
  range = "",
  test = "ktea3",
  test_name = "KTEA-3",
  domain = "Academic Skills",
  subdomain = "",
  narrow = "",
  pass = "",
  verbal = "",
  timed = "",
  test_type = "npsych_test",
  score_type = "standard_score",
  description = "",
  result = ""
)
```

## Test score ranges

```{r range}
table1 <- bwu::gpluck_make_score_ranges(table = table1, test_type = "npsych_test")
table2 <- bwu::gpluck_make_score_ranges(table = table2, test_type = "npsych_test")
```

## Domains for language tests

```{r}
table2 <-
  table2 |>
  mutate(
    domain = case_when(
      scale == "Oral Language Composite" ~ "Verbal/Language",
      scale == "Associational Fluency" ~ "Verbal/Language",
      scale == "Listening Comprehension" ~ "Verbal/Language",
      scale == "Oral Expression" ~ "Verbal/Language",
      scale == "Oral Fluency Composite" ~ "Verbal/Language",
      scale == "Comprehension Composite" ~ "Verbal/Language",
      scale == "Listening Comprehension" ~ "Verbal/Language",
      scale == "Expression Composite" ~ "Verbal/Language",
      TRUE ~ as.character(domain)
    )
  )
```

## Subdomains

```{r}
table1 <-
  table1 |>
  mutate(
    subdomain = case_when(
      scale == "Academic Skills Battery (ASB) Composite" ~ "Academic Achievement",
      scale == "Reading Composite" ~ "Reading",
      scale == "Math Composite" ~ "Math",
      scale == "Written Language Composite" ~ "Writing",
      scale == "Math Concepts & Applications" ~ "Math",
      scale == "Letter & Word Recognition" ~ "Reading",
      scale == "Written Expression" ~ "Writing",
      scale == "Math Computation" ~ "Math",
      scale == "Spelling" ~ "Writing",
      scale == "Reading Comprehension" ~ "Reading",
      TRUE ~ as.character(subdomain)
    )
  )

table2 <-
  table2 |>
  mutate(
    subdomain = case_when(
      scale == "Sound-Symbol Composite" ~ "Reading",
      scale == "Phonological Processing" ~ "Reading",
      scale == "Nonsense Word Decoding" ~ "Reading",
      scale == "Decoding Composite" ~ "Reading",
      scale == "Reading Fluency Composite" ~ "Reading",
      scale == "Silent Reading Fluency" ~ "Reading",
      scale == "Word Recognition Fluency" ~ "Reading",
      scale == "Decoding Fluency" ~ "Reading",
      scale == "Reading Understanding Composite" ~ "Reading",
      scale == "Reading Vocabulary" ~ "Reading",
      scale == "Oral Language Composite" ~ "Language",
      scale == "Associational Fluency" ~ "Expressive Language",
      scale == "Listening Comprehension" ~ "Receptive Language",
      scale == "Oral Expression" ~ "Expressive Language",
      scale == "Oral Fluency Composite" ~ "Expressive Language",
      scale == "Object Naming Facility" ~ "Reading",
      scale == "Comprehension Composite" ~ "Receptive Language",
      scale == "Listening Comprehension" ~ "Receptive Language",
      scale == "Expression Composite" ~ "Expressive Language",
      scale == "Orthographic Processing Composite" ~ "Reading",
      scale == "Letter Naming Facility" ~ "Reading",
      scale == "Academic Fluency Composite" ~ "Academic Fluency",
      scale == "Writing Fluency" ~ "Writing",
      scale == "Math Fluency" ~ "Math",
      scale == "Math Concepts & Applications" ~ "Math",
      scale == "Letter & Word Recognition" ~ "Reading",
      scale == "Written Expression" ~ "Writing",
      scale == "Math Computation" ~ "Math",
      scale == "Spelling" ~ "Writing",
      scale == "Reading Comprehension" ~ "Reading",
      TRUE ~ as.character(subdomain)
    )
  )
```

## Narrow subdomains

```{r}
table1 <-
  table1 |>
  mutate(
    narrow = case_when(
      scale == "Academic Skills Battery (ASB) Composite" ~ "General Academic Achievement",
      scale == "Math Concepts & Applications" ~ "Mathematical Knowledge",
      scale == "Letter & Word Recognition" ~ "Reading Decoding",
      scale == "Written Expression" ~ "Writing Ability",
      scale == "Math Computation" ~ "Mathematical Achievement",
      scale == "Spelling" ~ "Spelling Ability",
      scale == "Reading Comprehension" ~ "Reading Comprehension",
      scale == "Reading Composite" ~ "Reading Ability",
      scale == "Math Composite" ~ "Quantitative Reasoning",
      scale == "Written Language Composite" ~ "Written Language Ability",
      TRUE ~ as.character(narrow)
    )
  )

table2 <-
  table2 |>
  mutate(
    narrow = case_when(
      scale == "Academic Fluency Composite" ~ "Rate of Test-Taking",
      scale == "Sound-Symbol Composite" ~ "Phonological Processing",
      scale == "Decoding Composite" ~ "Reading Decoding",
      scale == "Reading Fluency Composite" ~ "Reading Speed",
      scale == "Reading Understanding Composite" ~ "Reading Comprehension",
      scale == "Oral Language Composite" ~ "Comprehension-Knowledge",
      scale == "Oral Fluency Composite" ~ "Communication Ability",
      scale == "Comprehension Composite" ~ "Comprehension-Knowledge",
      scale == "Expression Composite" ~ "Comprehension-Knowledge",
      scale == "Orthographic Processing Composite" ~ "Reading and Writing",
      scale == "Phonological Processing" ~ "Phonetic Coding",
      scale == "Nonsense Word Decoding" ~ "Reading Decoding",
      scale == "Silent Reading Fluency" ~ "Reading Speed",
      scale == "Word Recognition Fluency" ~ "Reading Speed",
      scale == "Decoding Fluency" ~ "Reading Speed",
      scale == "Reading Vocabulary" ~ "Reading Comprehension",
      scale == "Associational Fluency" ~ "Ideational Fluency",
      scale == "Oral Expression" ~ "Communication Ability",
      scale == "Object Naming Facility" ~ "Naming Facility",
      scale == "Listening Comprehension" ~ "Listening Ability",
      scale == "Letter Naming Facility" ~ "Naming Facility",
      scale == "Writing Fluency" ~ "Writing Speed",
      scale == "Math Fluency" ~ "Number Facility",

      scale == "Math Concepts & Applications" ~ "Mathematical Knowledge",
      scale == "Letter & Word Recognition" ~ "Reading Decoding",
      scale == "Written Expression" ~ "Writing Ability",
      scale == "Math Computation" ~ "Mathematical Achievement",
      scale == "Spelling" ~ "Spelling Ability",
      scale == "Reading Comprehension" ~ "Reading Comprehension",
      TRUE ~ as.character(narrow)
    )
  )
```

## PASS model

```{r}
table1 <-
  table1 |>
  mutate(
    pass = case_when(
      scale == "Academic Skills Battery (ASB) Composite" ~ "",
      scale == "Math Concepts & Applications" ~ "Simultaneous",
      scale == "Letter & Word Recognition" ~ "Sequential",
      scale == "Written Expression" ~ "Sequential",
      scale == "Math Computation" ~ "Simultaneous",
      scale == "Spelling" ~ "Sequential",
      scale == "Reading Comprehension" ~ "Sequential",
      scale == "Reading Composite" ~ "Sequential",
      scale == "Math Composite" ~ "Simultaneous",
      scale == "Written Language Composite" ~ "Sequential",
      TRUE ~ as.character(pass)
    )
  )

table2 <-
  table2 |>
  mutate(
    pass = case_when(
      scale == "Nonsense Word Decoding" ~ "Sequential",
      scale == "Academic Fluency Composite" ~ "Sequential",
      scale == "Writing Fluency" ~ "Sequential",
      scale == "Math Fluency" ~ "Simultaneous",
      scale == "Decoding Fluency" ~ "Sequential",
      scale == "Sound-Symbol Composite" ~ "Sequential",
      scale == "Phonological Processing" ~ "Simultaneous",
      scale == "Decoding Composite" ~ "Sequential",
      scale == "Reading Fluency Composite" ~ "Sequential",
      scale == "Silent Reading Fluency" ~ "Sequential",
      scale == "Word Recognition Fluency" ~ "Sequential",
      scale == "Reading Understanding Composite" ~ "Sequential",
      scale == "Reading Vocabulary" ~ "Sequential",
      scale == "Oral Language Composite" ~ "Sequential",
      scale == "Associational Fluency" ~ "Sequential",
      scale == "Listening Comprehension" ~ "Sequential",
      scale == "Oral Expression" ~ "Sequential",
      scale == "Oral Fluency Composite" ~ "Sequential",
      scale == "Object Naming Facility" ~ "Sequential",
      scale == "Comprehension Composite" ~ "Sequential",
      scale == "Listening Comprehension" ~ "Sequential",
      scale == "Expression Composite" ~ "Sequential",
      scale == "Letter Naming Facility" ~ "Sequential",
      scale == "Orthographic Processing Composite" ~ "Sequential",
      TRUE ~ as.character(pass)
    )
  )
```

## Verbal vs Nonverbal

```{r}
table1 <-
  table1 |>
  mutate(
    verbal = case_when(
      scale == "Academic Skills Battery (ASB) Composite" ~ "",
      scale == "Math Concepts & Applications" ~ "",
      scale == "Math Computation" ~ "Nonverbal",
      scale == "Math Composite" ~ "",
      TRUE ~ as.character(verbal)
    )
  )

table2 <-
  table2 |>
  mutate(
    verbal = case_when(
      scale == "Academic Fluency Composite" ~ "",
      scale == "Writing Fluency" ~ "",
      scale == "Math Fluency" ~ "Nonverbal",
      scale == "Silent Reading Fluency" ~ "",
      TRUE ~ as.character(verbal)
    )
  )
```

## Timed vs Untimed

```{r}
table2 <-
  table2 |>
  mutate(
    timed = case_when(
      scale == "Nonsense Word Decoding" ~ "Untimed",
      scale == "Academic Fluency Composite" ~ "Timed",
      scale == "Writing Fluency" ~ "Timed",
      scale == "Math Fluency" ~ "Timed",
      scale == "Decoding Fluency" ~ "Timed",
      scale == "Sound-Symbol Composite" ~ "Untimed",
      scale == "Phonological Processing" ~ "Untimed",
      scale == "Decoding Composite" ~ "Untimed",
      scale == "Reading Fluency Composite" ~ "Timed",
      scale == "Silent Reading Fluency" ~ "Timed",
      scale == "Word Recognition Fluency" ~ "Timed",
      scale == "Reading Understanding Composite" ~ "Untimed",
      scale == "Reading Vocabulary" ~ "Untimed",
      scale == "Oral Language Composite" ~ "Untimed",
      scale == "Associational Fluency" ~ "Untimed",
      scale == "Listening Comprehension" ~ "Untimed",
      scale == "Oral Expression" ~ "Timed",
      scale == "Oral Fluency Composite" ~ "Untimed",
      scale == "Object Naming Facility" ~ "Timed",
      scale == "Comprehension Composite" ~ "Untimed",
      scale == "Listening Comprehension" ~ "Untimed",
      scale == "Expression Composite" ~ "Untimed",
      scale == "Letter Naming Facility" ~ "Timed",
      scale == "Orthographic Processing Composite" ~ "Untimed",
      TRUE ~ as.character(timed)
    )
  )
```

## Descriptions

```{r}
table1 <-
  table1 |>
  mutate(
    description = case_when(
      scale == "Academic Skills Battery (ASB) Composite" ~ "Overall academic achievement in the areas of reading, math, and writing",
      scale == "Math Concepts & Applications" ~ "Applying mathematical principles to real-life situations, ranging from basic concepts, everyday applications, geometry, and algebra",
      scale == "Letter & Word Recognition" ~ "Single word reading/decoding of a list of regular and irregular words",
      scale == "Written Expression" ~ "Overall written expression skills including spelling and expository/contextual writing",
      scale == "Math Computation" ~ "Paper and pencil math calculation skills, ranging from basic operations with integers to geometry, algebra, and calculus problems",
      scale == "Spelling" ~ "Written spelling of words from dictations",
      scale == "Reading Comprehension" ~ "Reading comprehension skills at the level of word, sentence, and passage",
      scale == "Reading Composite" ~ "Composite score of decoding and comprehension that balances word-level and text-level reading skills",
      scale == "Math Composite" ~ "Estimate of overall mathematics skills in the domains of math comprehension and problem solving and math computation",
      scale == "Written Language Composite" ~ "Overall written expression skills including spelling and expository/contextual writing",
      TRUE ~ as.character(description)
    )
  )


table2 <-
  table2 |>
  mutate(
    description = case_when(
      scale == "Nonsense Word Decoding" ~ "Phonic decoding skills by reading aloud a list of pseudowords",
      scale == "Academic Fluency Composite" ~ "Overall academic fluency in reading, math, and writing",
      scale == "Writing Fluency" ~ "Sentence level writing fluency",
      scale == "Math Fluency" ~ "Overall speed/fluency in solving fact-based addition, subtraction, and multiplication problems",
      scale == "Decoding Fluency" ~ "Phonic decoding fluency",
      scale == "Sound-Symbol Composite" ~ "Composite measure of reading and spelling skills??",
      scale == "Phonological Processing" ~ "Auditory processing of phonemic proficiency and phonic decoding skills",
      scale == "Decoding Composite" ~ "Composite estimate of decontextualized phonic decoding and word reading skills",
      scale == "Reading Fluency Composite" ~ "General reading speed/fluncy",
      scale == "Silent Reading Fluency" ~ "Non oral reading fluency",
      scale == "Word Recognition Fluency" ~ "Orthographic lexicon, or sight vocabulary fluency",
      scale == "Reading Understanding Composite" ~ "Reading comprehension skills at the level of word, sentence, and passage",
      scale == "Reading Vocabulary" ~ "Vocabulary reading comprehension",
      scale == "Oral Language Composite" ~ "Overall estimate of receptive and expressive language skills at the level of the word, sentence, passage, and discourse",
      scale == "Associational Fluency" ~ "Semantic word fluency",
      scale == "Listening Comprehension" ~ "Receptive language comprehension at the level of the word, sentence, and passage",
      scale == "Oral Expression" ~ "Oral expression at the level of the word and sentence",
      scale == "Oral Fluency Composite" ~ "General expressive language fluency",
      scale == "Object Naming Facility" ~ "Rapid automatic naming (objects)",
      scale == "Comprehension Composite" ~ "Estimate of general language comprehension skills",
      scale == "Listening Comprehension" ~ "Receptive language comprehension at the level of the word, sentence, and passage",
      scale == "Expression Composite" ~ "Estimate of oral language expression skills",
      scale == "Letter Naming Facility" ~ "Rapid automatic naming (letters)",
      scale == "Orthographic Processing Composite" ~ "Overall measure of orthographic processing, including the size of the examinees orthographic lexicon and the quality of orthographic representations",
      TRUE ~ as.character(description)
    )
  )
```

## Glue results

```{r}
table1 <-
  table1 %>%
  tidytable::mutate(
    result = glue::glue(
      "{description} was {range}."
    )
  )

table2 <-
  table2 %>%
  tidytable::mutate(
    result = glue::glue(
      "{description} was {range}."
    )
  )
```

# Finalize

## Relocate variables

```{r}
table1 <- table1 |> dplyr::relocate(c(test, test_name), .before = scale)
table2 <- table2 |> dplyr::relocate(c(test, test_name), .before = scale)
```

## Merge tables

```{r}
ktea3 <- rbind(table1, table2)
```

## Add patient initials

```{r}
ktea3$patient <- patient
```

## Remove rows with no data

```{r}
ktea3 <- ktea3 |> 
  dplyr::filter(!is.na(description) & description != "") |> 
  dplyr::filter(!is.na(score) & score != "")
```

## Write out final csv

```{r}
readr::write_csv(ktea3, here::here("data", "csv", "ktea3.csv"), col_names = TRUE, na = "")
```
